ProteInfer, deep neural networks for protein functional inference

### 2023-02-28 latex/draft3.tex
bracket issues

The same trends for the relative performance of different approaches were seen for each of the direct-acyclic graphs that make up the GO ontology (biological process, cellular component and molecular function), but there were substantial differences in absolute performance (\Cref{sup:fig:go_ontologies}%htmlver: (see <a href="./latex/supplement.pdf">supplement</a>)
). Performance was highest for molecular function (max F1: 0.94), followed by biological process (max F1:0.86) and then cellular component (max F1:0.84).

>>>>

The same trends for the relative performance of different approaches were seen for each of the direct-acyclic graphs that make up the GO ontology (biological process, cellular component and molecular function), but there were substantial differences in absolute performance (\Cref{sup:fig:go_ontologies}%htmlver: see <a href="./latex/supplement.pdf">supplement</a>
). Performance was highest for molecular function (max F1: 0.94), followed by biological process (max F1:0.86) and then cellular component (max F1:0.84).
